\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-24 manuscript.Rnw
Update given that 'intercept' columns returned by create_params.flexsurvreg() in hesim are now named 'intercept'

<<psm_survmods_params>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples)
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
@

Survival curves for both PFS and OS are predicted using the \code{PsmCurves} class, which is setup using the input data and the parameters of the Weibull model. However, since we manually created the parameter object---meaning that the model terms were not generated using a formula interface---the input data must contain each term contained in the parameter object. We must consequently create an intercept column of ones.

<<psm_survmods>>=
# To remove with update of package
colnames(survmods_params$pfs$coefs$shape)[1] <- "intercept"
colnames(survmods_params$pfs$coefs$scale)[1] <- "intercept"
colnames(survmods_params$os$coefs$shape)[1] <- "intercept"
colnames(survmods_params$os$coefs$scale)[1] <- "intercept"

# To keep
survmods_data[, intercept := 1]
survmods <- create_PsmCurves(survmods_params, 
                             input_data = survmods_data)
@

>>>>

<<psm_survmods_params>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples)
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
survmods_params$pfs$coefs$scale[1:2, ]
@

Survival curves for both PFS and OS are predicted using the \code{PsmCurves} class, which is setup using the input data and the parameters of the Weibull model. However, since we manually created the parameter object---meaning that the model terms were not generated using a formula interface---the input data must contain each term contained in the parameter object. We must consequently create a column of ones for the ``intercept``.

<<psm_survmods>>=
survmods_data[, intercept := 1]
survmods <- create_PsmCurves(survmods_params, 
                             input_data = survmods_data)
@
